WSClean: an implementation of a fast, generic wide-field imager

### 2014-03-17 articles/2014/Article-WSClean/wsclean.tex
Slight rewording

Table~\ref{tbl:accuracy-measurements} lists the measured root mean square (RMS) in the residual image and the standard errors of the source brightnesses as detected by \textsc{Aegean}. \textsc{wsclean} is more accurate: it shows 2-33\% lower errors in the source fluxes and produces 0-49\% lower RMS noise compared to \textsc{casa}. The large residual RMS twice for \textsc{casa} at zenith is caused by the fact that we keep the number of $w$-projection planes in $w$-projection equal to the number of $w$-layers in $w$-stacking, resulting in only 12 $w$-planes at zenith. This evidently has a stronger effect on the $w$-projection algorithm. However, the computational performance of the $w$-projection algorithm is hardly affected by the number of $w$-projection planes, and in practical situations one would always use more $w$-projection planes. When 128 $w$-projection planes are used in \textsc{casa}, the residual RMS is equal to \textsc{wsclean} with 12 $w$-layers, but the flux density measurements are less accurate. We do not know why this parameter needs to be higher in \textsc{casa} to reach the same RMS. We are using enough $w$-planes to cover the sources: Eq.~\eqref{eq:nwlayers-bound} results in $N_\textrm{wlay}\gg 6$ for the top-left image pixel that is 26\degree away from the centre, while the sources are all within 10\degree. Also unexpected is that the source flux density becomes worse by increasing the number of planes. For \textsc{wsclean} both values stay approximately the same when the number of $w$-layers is increased.

>>>>

Table~\ref{tbl:accuracy-measurements} lists the measured root mean square (RMS) in the residual image and the standard errors of the source brightnesses as detected by \textsc{Aegean}. \textsc{wsclean} is more accurate: it shows 2-33\% lower errors in the source fluxes and produces 0-49\% lower RMS noise compared to \textsc{casa}. The large residual RMS for \textsc{casa} at zenith is caused by the fact that we keep the number of $w$-projection planes in $w$-projection equal to the number of $w$-layers in $w$-stacking, resulting in only 12 $w$-planes at zenith. This evidently has a stronger effect on the $w$-projection algorithm. However, the computational performance of the $w$-projection algorithm is hardly affected by the number of $w$-projection planes, and in practical situations one would always use more $w$-projection planes. When 128 $w$-projection planes are used in \textsc{casa}, the residual RMS is equal to \textsc{wsclean} with 12 $w$-layers, but the flux density measurements are less accurate. We do not know why this parameter needs to be higher in \textsc{casa} to reach the same RMS. We are using enough $w$-planes to cover the sources: Eq.~\eqref{eq:nwlayers-bound} results in $N_\textrm{wlay}\gg 1$ for the source furthest from the phase centre. Also unexpected is that the source flux density becomes worse by increasing the number of planes. For \textsc{wsclean} both values stay approximately the same when the number of $w$-layers is increased.
